On the computational complexity of detecting possibilistic locality

### 2017-06-19 paper.tex
Making a start moving some content into "background" section.

In 1991, Avis \emph{et al} \cite{Avis2004} demonstrated that determining whether or not a given table of these operational predictions for a Bell experiment had a local hidden variable explanation was \textbf{NP}-hard, building on work by Pitowsky \cite{Pito1991}. In this paper, we consider a more extreme, possibilistic, manifestation of nonlocality; one in which it is not only true that we cannot account for the specific experimental probabilities with a local hidden variable model, but that we cannot even account for the possibilities. In doing so, we will identify the minimal operational requirements for this problem to remain \textbf{NP}-hard, filling in the final gap in a categorisation started by Mansfield and Fritz \cite{Mans2011,Mans2016} and continued by Abramsky, Gottlob and Kolaitis \cite{Abra2013}. This nonlocality is a feature only of the table of possibilities at hand, with no dependence on the source of the correlations. Accordingly, the first sections of this paper will focus only on the decision problem at hand, with little consideration to how these correlations might arise, and so does not require any specialist knowledge of quantum theory. In the final section, we turn our focus to those data tables accessible within quantum theory, and demonstrate how we can embed a large set of \textsc{3-SAT} problems into a quantum formalism.

@@

%Introduce basic concepts here.

>>>>

In 1991, Avis \emph{et al} \cite{Avis2004} demonstrated that determining whether or not a given table of these operational predictions for a Bell experiment had a local hidden variable explanation was \textbf{NP}-hard, building on work by Pitowsky \cite{Pito1991}. In this paper, we consider a more extreme, possibilistic, manifestation of nonlocality; one in which it is not only true that we cannot account for the specific experimental probabilities with a local hidden variable model, but that we cannot even account for the possibilities. In doing so, we will identify the minimal operational requirements for this problem to remain \textbf{NP}-hard, filling in the final gap in a categorisation started by Mansfield and Fritz \cite{Mans2011,Mans2016} and continued by Abramsky, Gottlob and Kolaitis \cite{Abra2013}. This nonlocality is a feature only of the table of possibilities at hand, with no dependence on the source of the correlations. Accordingly, the first sections of this paper will focus only on the decision problem at hand, and no knowledge about how such a table might be calculated within the formalism of quantum mechanics is required. In the final section, we turn our focus to those data tables accessible within quantum theory, and demonstrate how we can embed a large set of \textsc{3-SAT} problems into a quantum formalism.

@@

In a Bell experiment, two researchers, canonically referred to as Alice and Bob, are placed at spacelike separated locations and perform experiments on a pair of quantum systems that may have interacted in the past. Each of the experimenters can choose between a range of measurement selections: Alice chooses an $a\in A$, Bob chooses a $b\in B$. Alice's measurement can take different outcomes $\{1,2,\dots,l\}$, and Bob's has possible outcomes $\{1,2,\dots,m\}$. If Alice and Bob have $k$ different measurement choices, and each has a maximum of $l$ different measurement outcomes (that is, $l=m$), this is known as a $(2,k,l)$ scenario \cite{Mans2011}: there are two parties, with access to $k$ measurements, each with $l$ different outcomes.

Each combination of measurement settings and measurement outcomes corresponds to an event, and quantum mechanics gives us the ability to calculate the probabilities that a specific pair of measurement outcomes will be observed, given the measurement settings. We can present these in a table, for example in Figure \ref{CHSH}.%Note. Pick consistent way of referring to outcome labelling etc.
